---
title: "Swirl tutorial (startup)"
author: "Jerid Francom"
date: "Tuesday August 2, 2016"
output: 
  html_document: 
    number_sections: yes
    theme: journal
    toc: yes
---

```{r startup, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# Startup

First find out what directory you will be loading the course from
```{r eval = TRUE}
getwd()
```

Then load the library

```{r eval = TRUE}
library(swirl)
library(swirlify) # start up `swirlify`
```

Now you can create a new course and lesson sheet.

```{r}
new_lesson("My Lesson", "My Course") # create new lesson
```

To resume working on an existing lesson (note that you make reference to the .yaml file)
```{r}
set_lesson("My_Course/My_Lesson/lesson.yaml")
```

To find out what lesson you're working on...

```{r}
get_current_lesson()
```

# Course structure

A `MANIFEST` file lists the order of the lessons for students. To add a current lesson to that file.


```{r}
add_to_manifest()
```


To include data to be used in lessons, you should add this function to the `initLesson.R` file:

```
.get_course_path <- function(){
  tryCatch(swirl:::swirl_courses_dir(),
           error = function(c) {file.path(find.package("swirl"),"Courses")}
  )
}
```

Then using `.get_course_path()` and `file.path()` you can add data to the lesson.

```
.get_course_path <- function(){
  tryCatch(swirl:::swirl_courses_dir(),
           error = function(c) {file.path(find.package("swirl"),"Courses")}
  )
}

dataset <- read.csv(file.path(.get_course_path(), "My_Course", "My_Lesson", "data.csv"))
```

The dataset will then be ready for the student on loading the lesson.^[Question: where to put the `data.csv` file? Should it go in `My_Course/data/data.csv`]

# Writing lessons

## General structure

Lessons are sequences of questions of the following general structure:

```
- Class: [type of question]
  Key1: [value1]
  Key2: [value2]

- Class: [type of question]
  Key1: [value1]
  Key2: [value2]
...
```

Questions have a `-` marking them as questions and a class associated. 

The first question in all lessons is a "meta question" which provides the basic information about the course.

```
- Class: meta
  Course: My Course
  Lesson: My Lesson
  Author: Dr. Jerid Francom
  Type: Standard
  Organization: Wake Forest University
  Version: 2.5
```

## Message questions

You can add `text` class questions using the following function in the console.

- `wq_message("Message goes here!")` 

## Command questions

A command question prompts a student to add an expression at the console.

```{r eval=TRUE}
args(wq_command)
```

```
- Class: cmd_question
  Output: Add 2 and 2 together using the addition operator.
  CorrectAnswer: 2 + 2
  AnswerTests: omnitest(correctExpr='2 + 2')
  Hint: Just type 2 + 2.
```

## Multiple choice questions

Options are presented in a different order each time. `AnswerChoices` list should be separated by semicolons `;`.

- `wq_multiple()` function

```{r eval=TRUE}
args(wq_multiple)
```

```
- Class: mult_question
  Output: What is the capital of Canada?
  AnswerChoices: Toronto;Montreal;Ottawa;Vancouver
  CorrectAnswer: Ottawa
  AnswerTests: omnitest(correctVal='Ottawa')
  Hint: This city contains the Rideau Canal.
```

## Figure questions

These questions are designed to display figures to students. `Figure` is an `.R` script that will draw the figure. `FigureType` is either `new` or `add`, where 'new' creates a new figure and 'add' adds a layer to the existing figure.

- `wq_figure()`

```{r eval=TRUE}
args(wq_figure)
```

```
- Class: figure
  Output: Look at this figure!
  Figure: draw.R
  FigureType: new
```

## Video/ URL questions

`VideoLink` is a URL that will be opened in a browser.

- `wq_video()`

```{r eval=TRUE}
args(wq_video)
```

```
- Class: video
  Output: Do you want to go to Google?
  VideoLink: https://www.google.com/
```

## Numerical questions

- `wq_numerical()`

```{r eval=TRUE}
args(wq_numerical)
```

```
- Class: exact_question
  Output: How many of the Rings of Power were forged by the elven-smiths of
    Eregion?
  CorrectAnswer: 19
  AnswerTests: omnitest(correctVal = 19)
  Hint: Three Rings for the Elven-kings under the sky, Seven for the Dwarf-lords
  in their halls of stone, Nine for Mortal Men doomed to die...
```

## Text questions

- `wq_text()`

```{r eval=TRUE}
args(wq_text)
```

```
- Class: text_question
  Output: What is the name of the programming language invented by 
    John Chambers?
  CorrectAnswer: 'S'
  AnswerTests: omnitest(correctVal = 'S')
  Hint: What comes after R in the alphabet?
```

## Script Questions

> Script questions might be the hardest questions to write, however the payoff in a student’s understanding of how R works is proportional. Script questions require that you write a custom answer test in order to evaluate the correctness of a script that a student has written. Writing custom answer tests is covered thoroughly in the answer testing section.

`Script` is an `.R` script that will be opened with the student reaches the question. This script needs to be in a subdirectory `scripts` in the lesson folder. Another version of this script which contains the correct answer should also appear.

```
scripts/
-------script.R
-------script-correct.R
```

An example: `fib.R`

```
# Write a function that returns the nth fibonacci number. Think about
# what we just reviewed with regard to writing recurisive functions.

fib <- function(n){
  # Write your code here.
}
```

And the correct version: `fib-correct.R`

```
# Write a function that returns the nth fibonacci number. Think about
# what we just reviewed with regard to writing recurisive functions.

fib <- function(n){
  if(n == 0 || n == 1){
    return(n)
  } else {
    return(fib(n-2) + fib(n-1))
  }
}
```

Here's the custom test file `custom_tests.R` which includes the `test_fib()` function:^[I'm going to need to do some looking into how to create custom tests!]

```
test_fib <- function() {
  try({
    func <- get('fib', globalenv())
    t1 <- identical(func(1), 1)
    t2 <- identical(func(20), 6765)
    t3 <- identical(sapply(1:12, func), c(1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144))
    ok <- all(t1, t2, t3)
  }, silent = TRUE)
  exists('ok') && isTRUE(ok)
}
```

- `wq_script()`

```{r eval=TRUE}
args(wq_script)
```

## Answer testing

Answer testing determines if a student's answer is correct. A correct answer results in an answer test with a value of `TRUE`. If `FALSE` is returned, then the answer is considered incorrect. Swirl has provided many of the types of tests that authors/ teachers most likely will use. 

```
- Class: cmd_question
  Output: Assign the mean all the numbers from 1 to 10 to a variable called x.
  CorrectAnswer: x <- mean(1:10)
  AnswerTests: var_is_a('numeric', 'x');omnitest(correctExpr = 'x <- mean(1:10)')
  Hint: Just type x <- mean(1:10).
```

### Built-in answer tests

#### omnitest() 

The `omnitest()` function is by and large is the main function for answer testing. It can handle correct values, correct expressions, or both.

**Testing for an expression**

```
- Class: cmd_question
  Output: Plot the integers from 1 to 10.
  CorrectAnswer: plot(1:10)
  AnswerTests: omnitest(correctExpr = 'plot(1:10)')
  Hint: Try using the plot() function.
```

**Testing for a value**

```
- Class: cmd_question
  Output: Enter an expression that evaluates to the number 4.
  CorrectAnswer: 4
  AnswerTests: omnitest(correctVal = 4)
  Hint: Any expression will work as long as it evalualtes to 4!
```

**Testing for an expression or a value**

```
- Class: cmd_question
  Output: What's the result of adding 2 and 2?
  CorrectAnswer: 2 + 2
  AnswerTests: omnitest(correctExpr='2 + 2', correctVal = 4)
  Hint: Try using the addition operator.
```

#### any_of_exprs()

This function allows you to evaluate whether a student has used on of several expressions.

```
- Class: cmd_question
  Output: Enter an expression that creates a vector of all of the integers from
    1 to 10.
  CorrectAnswer: 1:10
  AnswerTests: any_of_exprs('1:10', 'seq(1, 10, 1)')
  Hint: Try using the colon operator.
```

#### expr_creates_var()

This function prevents a variable from being changed during a students answer.

```
- Class: cmd_question
  Output: Assign 10 to the variable x.
  CorrectAnswer: x <- 10
  AnswerTests: omnitest(correctExpr='x <- 10')
  Hint: Just type x <- 10.

- Class: cmd_question
  Output: Assign x*2 to the variable x.
  CorrectAnswer: x <- x*2
  AnswerTests: omnitest(correctExpr='x <- x*2');expr_creates_var('x')
  Hint: Just type x <- x*2.
```

#### expr_uses_func()

Tests whether a student has used a particular function in answering the question.

```
- Class: cmd_question
  Output: Use the mean() function to find the mean of any vector.
  CorrectAnswer: mean(1:10)
  AnswerTests: expr_uses_func('mean')
  Hint: Use the mean function with any numeric vector as an argument.
```

#### val_matches()

This function is used exclusively with text questions. It uses regular expressions to determine if the text answer is correct.

```
- Class: text_question
  Output: What is the capital of Chile?
  CorrectAnswer: Santiago
  AnswerTests: val_matches('[S|s]antiago')
  Hint: Ryhmes with Zandiago.
```

#### More

For more on `AnswerTests` view the [Swirl Course Network](http://swirlstats.com/scn/).

# Testing lessons

## Demoing a lesson

To start a lesson demo `demo_lesson()` will do it. You can also skip to a particular question by using `demo_lesson(from = 6)`, for example.

## Testing a lesson

Just run `test_lesson()` to test the general syntax and structure of the lesson. To test every lesson in a course `test_course()`. Messages will be printed to the console to alert of any problems.

# Sharing courses

## As a file

Create a `.swc` file for a course with `pack_course()` once your are in one of the lessons in the course. (You can check with `get_lesson()` and change with `set_lesson()`.)

The file produced can be shared like any other file, via email, dropbox, Sakai, etc. and then installed (interactively) with the `install_course()` function using the `swirl` package. 

## On GitHub

Developing on GitHub is good practice. It facilitates getting help from other 'swirlers' and makes the course instantly available. Using the `install_course_github()`. The course directory must be in the root of the git repository. 

You can browse some of the available courses on the [Swirl Course Network](http://swirlstats.com/scn/). 

## Swirl Course Network

This network aims to provide a repository for all publicly available Swirl courses. The [homepage](http://swirlstats.com/scn/) has more information.


1. Create an .swc file for your course.
2. Fork https://github.com/swirldev/scn on GitHub.
3. Add the .swc file to your fork.
3. Add an Rmd file to your fork like this one. You can include a description of your course, authors, a course website, and how to install your course.
4. Run rmarkdown::render_site() when your current directory is set to your fork.
5. Add, commit, and push your changes to GitHub, then send us a Pull Request.
6. After adding your course to the SCN students will be able to install your course using install_course("[Name of Your Course]") in swirl.

# Swirl in the classroom

## Logging student progress

Swirl can create a log of student progress for instructors to evaluate. Logging is disabled by default, but can be enabled in the `initLesson.R` file with `swirl_options(swirl_logging = TRUE)`.

One convenient method is through Google Forms.

## Using Google Forms

[Here is the documentation](https://github.com/seankross/Google_Forms_Course)